Title

### 2014-01-21 paper/parts/conclusions.tex
Minor tweaks to the conclusion.

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{graphicx}
\usepackage{multirow}

\begin{document}

@@

Our work has introduced a novel use of transfer entropy for the detection of activity-based communities. In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users. It is thus interesting that we find influence tends to be higher across community boundaries than within them. This counterintuitive result warrants further investigation. In addition, more rigorous choices of both the lag and time resolution based on methods for model selection should be explored~\cite{claeskens2008model}.

@@

\end{document}

>>>>

@@

Our work has introduced a novel use of transfer entropy for the detection of activity-based communities. In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users. Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}. In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.

@@

### 2014-01-21 paper/parts/methods.tex

Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., retweets and mentions). We do this through a metric we call (incoming/outgoing) information events. We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet of one of $u$'s tweets by another user in the network. The logic for this definition is as follows: if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers. In either case there was information outgoing from $u$ which affected the network in the some way. Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or as retweeting another user in the network.
%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets. [[Seeems out of place]]
%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it. 
With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average. 
We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users. %and whose link represent a user-follower relationship.
In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows. The final network consists of 6,917 nodes and 1,481,131 edges.

@@

\subsection{Topic-based Communities and Hashtag Weighting}
\label{sec:method-topic}

>>>>

Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., via retweets and mentions). We do this through a metric we call (incoming/outgoing) information events. We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet of one of $u$'s tweets by another user in the network. The logic for this definition is as follows: if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers. In either case there was information outgoing from $u$ which affected the network in the some way. Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or as retweeting another user in the network.
%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets. [[Seeems out of place]]
%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it. 
With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average. 
We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users. %and whose link represent a user-follower relationship.
In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows. The final network consists of 6,917 nodes and 1,481,131 edges.

@@

\subsection{Topic-Based Communities and Hashtag Weighting}
\label{sec:method-topic}
